Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-02 Grassmannian_cells.tex
no edits

Although it follows from the results of Hille, Huisgen-Zimmermann and Reineke that every projective variety can be realized as a quiver Grassmannian, 
%-- which is maybe not surprising as the classification problem of indecomposable quiver representations is wild -- 
it turns out that very interesting phenomena arise when restricting to certain quivers or representations with certain properties.
For instance, quiver Grassmannians attached to exceptional representations are smooth \cite{cr}.
For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition into affine spaces, see \cite{ce,lw} and references therein.
It has been conjectured\sayD{reference?} that this is also true for exceptional representations of any quiver, in particular for preprojective and preinjective representations.

>>>>

Although it follows from the results of Hille, Huisgen-Zimmermann and Reineke that every projective variety can be realized as a quiver Grassmannian, 
%-- which is maybe not surprising as the classification problem of indecomposable quiver representations is wild -- 
it turns out that very interesting phenomena arise when restricting to certain quivers or representations with certain properties.
For instance, quiver Grassmannians attached to exceptional representations are smooth \cite{cr}.
For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition into affine spaces, see \cite{ce,lw} and references therein.
It has been conjectured that this is also true for exceptional representations of any quiver, in particular for preprojective and preinjective representations.
